A Detection of the Environmental Dependence of the Sizes and Stellar Haloes of Massive Central Galaxies

### 2017-12-05 draft/paper2_v9.tex
New edits for Felipe's and Chris' comments

\begin{abstract}  We use ${\sim}100$ deg$^2$ of 
    deep ($>28.5$ \sb{} in $i$-band), high-quality 
    (median 0.6\asec seeing) imaging data from the Hyper Suprime--Cam (HSC) survey to reveal the halo mass dependence of the surface mass density profiles and outer stellar envelopes of massive galaxies. The $i$-band images from the HSC survey reach ${\sim}4$ magnitudes deeper than 
    Sloan Digital Sky Survey and enable us to directly trace stellar mass distributions 
    to 100 kpc without requiring stacking.  
    We conclusively show that, at fixed stellar mass, the stellar profiles of massive 
    galaxies depend on the masses of their dark matter haloes. 
    On average, massive central galaxies with \logmtot{}$>11.6$ in more massive haloes 
    at $0.3 < z < 0.5$ have shallower inner stellar mass density profiles 
    (within ${\sim}10$--$20$ kpc) and more prominent outer envelopes. 
    These differences translate into a halo mass dependence of the mass--size relation. Central galaxies in haloes with \logmh{}$>14.0$ are $\sim 20$\% larger in $R_{\mathrm{50}}$ at fixed \mtot{}. Such dependence is also reflected in the relationship between the stellar mass 
    within 10 and 100 kpc.  Comparing to the mass--size relation, the \mtot{}--\minn{} relation avoids the 
    ambiguity in the definition of size, and can be straightforwardly compared with 
    simulations. 
    Our results demonstrate that, with deep images from HSC, we can quantify the 
    connection between halo mass and the outer stellar halo, which may provide new 
    constraints on the formation and assembly of massive central galaxies.

@@

    There have been multiple observational attempts to test the two-phase 
    formation scenario using galaxies at low redshift, by investigating surface 
    brightness or mass density profiles (e.g., \citealt{Huang2013a, Huang2013b, 
    Oh2017}, optical colour gradients (e.g., \citealt{LaBarbera2010, LaBarbera2012}), 
    and stellar population gradients \citep[e.g.,][]{Coccato2010, Coccato2011, 
    Greene2015, Barbosa2016}. 
    \song{
    These observations are generally consistent with the two-phase formation scenario. 
    However, it is still not clear whether this picture correctly 
    predicts the connection between the stellar mass distributions in massive galaxies 
    and their dark matter haloes.}

     \song{In the $\Lambda$CDM cosmology, the assembly of massive ETGs is intrinsically 
    tied to the hierarchical growth of their host dark matter haloes 
    (e.g., \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
    Hydrodynamic simulations suggest that the fraction of stars accreted through 
    mergers (the \textit{ex situ} component) in central galaxies increases with halo 
    mass (e.g., \citealt{RodriguezGomez2016, Pillepich2017b}). 
    The major merger rate is not a strong function of progenitor halo mass 
    (e.g., \citealt{Shankar2015}) but minor mergers can still play an important 
    role in determining the structures of central galaxies 
    (e.g., \citealt{Guo2011, Yoon2017}). 
    Minor mergers are efficient at `puffing up' the outskirts of massive 
    galaxies (e.g., \citealt{Oogi2013, Bedorf2013}). 
    Because the minor merger rate increases with halo mass, the 
    structures of massive ETGs and the well-known stellar mass--effective radius 
    relation (\mstar{}--$R_{\rm e}$; e.g., \citealt{Shen2003, Guo2009}) should 
    depend on their `environment'\footnote{There are multiple definitions of 
    `environment' in the literature. 
    In this work, we use `environment' and halo mass interchangeably.}
    (e.g., \citealt{Shankar2013, Shankar2014}). 
    However, evidence for the environment-dependence of \mstar{}--$R_{\rm e}$
    at low redshift is still not very solid (\citealt{Nair2010, HCompany13}; 
    but also see \citealt{Yoon2017}), and the results at higher redshift are 
    even more unclear (e.g., \citealt{Papovich2012, Lani2013, Delaye2014}; but 
    also see \citealt{Rettura2010}).
    }

	\song{
    Deep images of massive galaxies can probe the outer stellar halos of massive 
    galaxies and test these predictions. 
    Unfortunately, this is observationally challenging since the stellar haloes 
    of massive galaxies can extend to $>100$ kpc (e.g., 
    \citealt{Tal2011, DSouza2014}), and their surface brightness profiles decline 
    rapidly with typical values of $\mu > 26.0$ \sb{} in $i$-band at 100 kpc and 
    at $z\sim0.3$. 
    }
    In \citet[][Paper I hereafter]{hscMassiveI}, we showed that deep, 
    multi-band imaging from the Subaru Strategic Program (SSP; \citealt{HSC-SSP,
    HSC-DR1}) using Hyper Suprime-Cam (HSC; \citealt{Miyazaki2012}, 
    Miyazaki in~prep.) allows us to extract robust surface stellar
    mass density (\mden{}) profiles for {\it individual} galaxies with 
    \logms{}$>11.4$ at $0.3 < z < 0.5$ and out to 100 kpc. 
    In Paper I, we characterized the stellar mass profiles of massive ETGs and 
    showed that there is a large intrinsic scatter in the stellar haloes of
    massive galaxies on 100-kpc scales. 
    In this paper, we investigate whether the large scatter in the outer 
    profiles of massive galaxies correlates with halo mass. 
    We conclusively show that the sizes and stellar haloes of massive central galaxies 
    depend on dark matter halo mass. 
    In other words, we reveal the halo mass dependence of the mass--size relation 
    for massive ETGs.

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_prof_1}
      \caption{
          The environmental dependence of the stellar mass profiles of massive central 
          galaxies. 
          Left: Halo mass dependence of galaxy profiles at fixed `total' stellar mass 
          (\mtot{}). 
          Right: Halo mass dependence of galaxy profiles at fixed `inner-mass' 
          (\minn{}). Orange and red lines correspond to central galaxies living in 
          haloes with \logmh{} $\geq 14.2$. 
          Black and grey lines correspond to central galaxies living in haloes with 
          \logmh{} $\leq 14.0$. 
          Thin lines show the profiles of individual galaxies, while thick lines show 
          the median profile. 
          The uncertainty on the median profile is given by the shaded region and is 
          computed via bootstrap resampling. 
          Brown lines in the bottom panels show the relative difference between  
          the two median profiles 
          ($\Delta = \log(\mu_{\star, \mathrm{cenHighMh}}) - 
          \log(\mu_{\star, \mathrm{cenLowMh}}$). 
          Errors in the difference between the two profiles are also computed 
          via bootstrap.
          The grey-shaded regions show a Monte Carlo test to assess how likely it is to 
          obtain $\Delta$ from random sub-samples of the data. 
          To compute the grey-shaded regions, we first mix the two samples 
          (\rbcg{} and \nbcg{}), then draw sub-samples of galaxies from the mixed 
          population and compute $\Delta$ in the same fashion as for our fiducial 
          signal. 
          We repeat this process 5000 times.  
          The dark grey--shaded region (light grey--shaded region) shows the 1-$\sigma$ 
          (3-$\sigma$) fluctuations in $\Delta$ from these 5000 draws.
          }
      \label{fig:prof_1} 
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    In Paper~I, we select a sample of 25286 bright galaxies with spectroscopic 
    redshifts or reliable `red-sequence' photometric redshifts (\citealt{Rykoff2014}) 
    at $0.3<z<0.5$. 
    Within this redshift range, we have a large enough volume 
    ($\sim5\times 10^6$ Mpc$^3$) to sample the galaxy stellar mass function above 
    \logms$>11.6$, and we can spatially resolve galaxies profiles to $\sim 5$ kpc 
    ($1.0^{\arcsec}$ corresponds to 4.4 and 6.1 kpc at $z=0.3$ and 0.5). 
    \song{
    Massive galaxies should experience little structural evolution and 
    size growth between $z=0.5$ and 0.3 ($\sim$1.5 Gyr time span) 
    based on model predictions (e.g., \citealt{Shankar2015}).
    }

@@

   We use these two simple metric masses to explore the \mstar{}-dependence of the 
   fraction of accreted stars and to reveal the diversity of stellar envelopes among 
   massive galaxies. 
   In practice, we also have the full profiles for each galaxy and can cast our 
   results in terms of the full stellar mass profiles. 
   However, in many cases we find it useful to display figures using the simpler 
   \minn{} and \mtot{} quantities. 
   In Figure \ref{fig:m100_m10_color}, we highlight the diversity of galaxies as a 
   function of \minn{} and \mtot{}. 
   Figure \ref{fig:m100_m10_color} shows a random subsample of massive galaxies with 
   very similar \minn{} that have a large range of \mtot{}. 
   We use these two aperture masses to guide our comparison of massive galaxies 
   as a function of environment.

@@

    In this work, we focus on massive galaxies with \mtot{} $>10^{11.6}$~\msun{}. 
    In Paper~I, we demonstrate that this sample is almost mass complete over our full 
    redshift range. 
    In addition to the mass cut above, we also limit our sample to galaxies that live 
    at the centers of their own dark matter haloes -- so-called `central' galaxies. 
    We use the \redm{} \texttt{v5.10} \citep{Rykoff2014, Rozo2015b} cluster catalogue 
    to help us construct two central galaxy samples.

@@

    First, we build a sample of central galaxies in high mass haloes. We select 68 massive central galaxies from \redm{} clusters 
    with richness $\lambda \geq 30$, with central probability $P_{\mathrm{Cen}} \geq 0.7$, and \logmtot{}$ >11.5$ 
    at $0.3 < z < 0.5$ (63/68 have \logmtot{}$ >11.6$). 
    This $\lambda$ limit is chosen to mitigate incompleteness in the cluster catalogue
    at the high end of our redshift window. 
    The $P_{\mathrm{Cen}}$ limit is imposed to limit our sample to central galaxies. 
    \song{
    \citet{Simet2017} present a calibration of the \mhalo{}-$\lambda$ relation for \redm{} 
    clusters using SDSS weak-lensing. Based on this calibration, our sample corresponds to central galaxies living 
    in haloes with \mhalo{}$>10^{14.2}$~\msun{}. 
    This calibration is consistent with several other independent calibrations 
    using different methods (e.g., \citealt{Saro2015, Farahi2016, 
    Melchior2016, Murata2017}). 
    }
    The median richness of the sample is $\lambda \approx 41$ 
    (\mhalo{}$\approx 2.2 \times 10^{14}$~\msun{}), and there are 44 central galaxies in clusters with $\lambda>50$ 
    (\mhalo{}$\approx 3.0 \times 10^{14}$~\msun{}).
    We refer to this sample of \textbf{central galaxies in massive haloes} as 
    the \rbcg{} sample.

    Second, we build a sample of central galaxies in low mass haloes. We begin by excluding all galaxies in \redm{} clusters with $\lambda > 20$.
    \song{
    We convert $\lambda$ to $M_{\mathrm{200b}}$ using the \citet{Simet2017} calibration. For each cluster, we compute $R_{\mathrm{200b}}$ using the \texttt{Colossus} Python package 
    (\citealt{Colossus})\footnote{\url{http://www.benediktdiemer.com/code/colossus/}}
    provided by \citet{Diemer2015}} 
    We exclude all galaxies within a cylinder around each cluster, with a radius
    equal to $R_{\mathrm{200b}}$, and a length equal to twice the value of the 
    photometric redshift uncertainty of the cluster (typically around 0.015 to 0.025).
    This second sample is dominated by central galaxies living in haloes with
    $M_{\mathrm{200b}} < 10^{14}$~\msun{}; we refer to this sample as \nbcg{}. \
    There are 833 central galaxies with \logmtot{}$> 11.6$ in this sample.

    Satellite contamination in our sample should be low (e.g., \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}). 
    For instance, the model from \citet{Saito2016} predicts that our \rbcg{} sample should only contain $\sim 7$\% satellites (corresponding to satellites with \logmtot{}$>11.6$ and living in haloes with \logmh$<14.0$).

@@

    Our analysis fails to extract 1-D profiles for $\sim10$\% of 
    \rbcg{} and \nbcg{} galaxies due to ongoing major mergers or projection effects 
    (e.g.\ nearby foreground galaxy or bright stars). 
    However, this small failure rate should not affect any of our results.

@@

    First, we ask whether the \mden{} profiles of massive central galaxies depend on 
    halo mass at fixed stellar mass.    
    We show comparisons of \mden{} profiles at both fixed \mtot{} and fixed 
    \minn{}. All comparisons are performed with a fixed underlying redshift
    distribution by matching samples in redshift in addition to stellar mass
    (see Appendix~\ref{app:match}, Appendix~\ref{app:redshift}, 
    and Fig~\ref{fig:match} for details).

@@

        \item Massive galaxies matched by \minn{} display a range of  \mtot{} values. Those in massive dark matter halos have more prominent outer stellar haloes. The scatter in the outer profiles observed in Figure \ref{fig:prof_1} is an \textit{intrinsic} scatter (not measurement error).                     
    \end{itemize}

@@

    In summary, we detect a subtle, but robust halo mass dependence of 
    the profiles of massive central galaxies. 
    This dependence could be driven by the fact that massive halos have a larger minor 
    merger rate compared to less massive haloes. 
    Nondissipative (minor) mergers should not strongly alter inner 
    profiles, but can efficiently build up outer haloes 
    (e.g., \citealt{Hilz2013}, \citealt{Oogi2013}).

@@

    \song{However, `size' is not a well-defined parameter for massive 
    galaxies with very extended stellar mass distributions. 
    In practice, measurements of the `effective radius', or `half-light radius', depend on resolution, depth, filter, and may also 
    depend on the adopted model for the light profile.  
    This makes comparisons of size measurements among different observations, 
    or between observations and models, uncertain. This is the main reason
    why we prefer to compare \mden{} profiles directly which completely bypasses the need to consider `size'.
    }

@@

    \song{
    We also compare with results from \citealt{HCompany13} (HC13b; green dashed line), 
    who studied $z\leq 0.09$ central ETGs in $12.5 \le$ \logmh{} $< 15$ haloes. 
    HC13b use the \citet{Yang2007} group catalog to estimate halo mass. 
    In contrast to the present study, HC13b find no environment dependence in the 
    mass--size relation for central galaxies. 
    They obtain effective radii from single-\ser{} model fitting to SDSS 
    images and derive stellar mass based on SED fitting using the BC03 (\citealt{BC03}) 
    synthetic population model. 
    We convert the HC13b \mstar{} estimates from a Kroupa IMF to a Chabrier 
    IMF by applying a constant $-0.05$ dex shift (see \citealt{Bernardi2016a}). 
    We further add $+0.1$dex to the HSC13 stellar masses to account for a systematic 
    offset between BC03 and our FSPS model (see Paper~1). Our overall mass-size relation is in good agreement with HC13a.}

@@

    We now investigate the relationship between \mtot{}, \minn{}, and \mhalo{}. 
    Compared to the mass--size relation, the \mtot{}--\minn{} relation is not plagued 
    by the ambiguity of galaxy `size', and it also enables a more straightforward 
    comparison with numerical simulations.

@@

    %Meanwhile, at fixed \minn{} -- a proxy for the \mstar{} of the `\textit{in situ}' 
    %component -- central galaxies in more massive haloes tend to be more massive and 
    %display more prominent stellar haloes. 
    %\song{
    %The comparison of \mden{} profiles for \minn{}-matched samples may not directly
    %reflect the environment-related processes because other physical mechanisms could 
    %also change the inner \mden{} profiles and their \mtot{} could be quite different. 
    %But the combination of \mtot{} and \minn{} clearly suggests that information about
    %their dark matter haloes or environments is encoded within this simple 2-D plane. 
    %We discuss more scientific implications of these results in 
    %\S~\ref{sec:discussion}
    %}

@@

    \begin{itemize}
        \item \song{
            The ellipticity profiles of massive central galaxies do not depend on 
            halo mass at fixed \mtot{} at $R<60$ kpc (upper left panel). 
            }

@@

    Using deep images from the HSC survey, we show that the stellar mass distributions 
    of massive central galaxies at $0.3 < z < 0.5$ depend on halo mass. At fixed total galaxy mass, central galaxies in massive halos have larger half-light radii and host more prominent outer 
    stellar haloes compared to galaxies in low mass haloes. We also find that 
    the outer stellar haloes ($R>50$ kpc) of massive galaxies show the strongest 
    variations with halo mass.

    \song{
    The two-phase formation scenario can qualitatively explain these results. 
    In this scenario, intense dissipative processes at $z > 2$ are responsible for the 
    formation of \textit{in situ} stars in massive central galaxies. 
    After a rapid quenching of star formation, the subsequent assembly of massive galaxiesis  dominated by the accretion of satellite galaxies through (mostly) 
    non--dissipative mergers. 
    Dry minor mergers are efficient at depositing \textit{ex situ} stars in the 
    outskirts of massive galaxies (e.g., \citealt{Oogi2013, Bedorf2013}) and hence in building up outer stellar haloes. The fact that minor mergers become more frequent in more massive dark matter haloes could lead to the halo mass dependence of galaxy profiles that we identify in Figure~\ref{fig:prof_1}.}

@@

Figure \ref{fig:scaling_relation} shows that, at fixed total galaxy mass, centrals in high mass haloes have slightly shallower inner \mden{} slopes lower values of \minn{} compared to those in low mass haloes. \song{We have tested that this cannot be solely explained by the choice of a finite aperture (100 kpc) to estimate `total' galaxy mass. Integrating our profiles our to larger radii makes the differences between \rbcg{} and \nbcg{} galaxies on the \mtot{}--\minn{} 
    plane even more significant \alexie{reference to somewhere in the appendix?}. In hydrodynamic simulations, intense dissipative processes help create a self-similar de~Vaucouleurs--like ($n{\sim} 4$) inner density profile (e.g., \citealt{Hopkins2008}). However, there are a variety of physical processes that can shape and alter the inner  profile which we now discuss.
    }

>>>>

\begin{abstract}

    We use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), high-quality 
    (median 0.6\asec seeing) imaging data from the Hyper Suprime--Cam (HSC) survey to 
    reveal the halo mass dependence of the surface mass density profiles and outer 
    stellar envelopes of massive galaxies. 
    The $i$-band images from the HSC survey reach ${\sim}4$ magnitudes deeper than 
    Sloan Digital Sky Survey and enable us to directly trace stellar mass distributions 
    to 100 kpc without requiring stacking.  
    We conclusively show that, at fixed stellar mass, the stellar profiles of massive 
    galaxies depend on the masses of their dark matter haloes. 
    On average, massive central galaxies with \logmtot{}$>11.6$ in more massive haloes 
    at $0.3 < z < 0.5$ have shallower inner stellar mass density profiles 
    (within ${\sim}10$--$20$ kpc) and more prominent outer envelopes. 
    These differences translate into a halo mass dependence of the mass--size relation. 
    Central galaxies in haloes with \logmh{}$>14.0$ are $\sim 20$\% larger in 
    $R_{\mathrm{50}}$ at fixed \mtot{}. 
    Such dependence is also reflected in the relationship between the stellar mass 
    within 10 and 100 kpc.  
    Comparing to the mass--size relation, the \mtot{}--\minn{} relation avoids the 
    ambiguity in the definition of size, and can be straightforwardly compared with 
    simulations. 
    Our results demonstrate that, with deep images from HSC, we can quantify the 
    connection between halo mass and the outer stellar halo, which may provide new 
    constraints on the formation and assembly of massive central galaxies.

@@

    There have been multiple observational attempts to test the two-phase 
    formation scenario using galaxies at low redshift, by investigating surface 
    brightness or mass density profiles (e.g., \citealt{Huang2013a, Huang2013b, 
    Oh2017}), optical colour gradients (e.g., \citealt{LaBarbera2010, LaBarbera2012}), 
    and stellar population gradients \citep[e.g.,][]{Coccato2010, Coccato2011, 
    Greene2015, Barbosa2016}. 
    \song{
    These observations are generally consistent with the two-phase formation scenario. 
    However, it is still not clear whether this picture correctly 
    predicts the connection between the stellar mass distributions in massive galaxies 
    and their dark matter haloes.}

    \song{In the $\Lambda$CDM cosmology, the assembly of massive ETGs is intrinsically 
    tied to the hierarchical growth of their host dark matter haloes 
    (e.g., \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
    Hydrodynamic simulations suggest that the fraction of stars accreted through 
    mergers (the \textit{ex situ} component) in central galaxies increases with halo 
    mass (e.g., \citealt{RodriguezGomez2016, Pillepich2017b}). 
    The major merger rate is not a strong function of progenitor halo mass 
    (e.g., \citealt{Shankar2015}) but minor mergers rate should increase with 
    halo mass, hence play an important role in determining the structures of central 
    galaxies (e.g., \citealt{Guo2011, Yoon2017}). 
    Minor mergers are efficient at `puffing up' the outskirts of massive 
    galaxies (e.g., \citealt{Oogi2013, Bedorf2013}). 
    Because the minor merger rate increases with halo mass, the 
    structures of massive ETGs and the well-known stellar mass--effective radius 
    relation (\mstar{}--$R_{\rm e}$; e.g., \citealt{Shen2003, Guo2009}) should 
    depend on their `environment'\footnote{There are multiple definitions of 
    `environment' in the literature. 
    In this work, we use `environment' and halo mass interchangeably.}
    (e.g., \citealt{Shankar2013, Shankar2014}). 
    However, evidence for the environment-dependence of \mstar{}--$R_{\rm e}$
    at low redshift is still not very solid (\citealt{Nair2010, HCompany13}; 
    but also see \citealt{Yoon2017}), and the results at higher redshift are 
    even more unclear (e.g., \citealt{Papovich2012, Lani2013, Delaye2014}; but 
    also see \citealt{Rettura2010}).
    }

	\song{
    Deep images of massive galaxies can probe their outer stellar halos of massive 
    galaxies and test these predictions. 
    Unfortunately, this is observationally challenging since the stellar haloes 
    of massive galaxies can extend to $>100$ kpc (e.g., 
    \citealt{Tal2011, DSouza2014}), and their surface brightness profiles decline 
    rapidly with typical values of $\mu > 26.0$ \sb{} in $i$-band at 100 kpc and 
    at $z\sim0.3$. 
    }
    In \citet[][Paper I hereafter]{hscMassiveI}, we showed that deep, 
    multi-band imaging from the Subaru Strategic Program (SSP; \citealt{HSC-SSP,
    HSC-DR1}) using Hyper Suprime-Cam (HSC; \citealt{Miyazaki2012}, 
    Miyazaki in~prep.) allows us to extract robust surface stellar
    mass density (\mden{}) profiles for {\it individual} galaxies with 
    \logms{}$>11.4$ at $0.3 < z < 0.5$ and out to 100 kpc. 
    In Paper I, we characterized the stellar mass profiles of massive ETGs and 
    showed that there is a large intrinsic scatter in the stellar haloes of
    massive galaxies on 100-kpc scales. 
    In this paper, we investigate whether the large scatter in the outer 
    profiles of massive galaxies correlates with halo mass. 
    We conclusively show that the sizes and stellar haloes of massive central 
    galaxies depend on dark matter halo mass. 
    In other words, we reveal the halo mass dependence of the mass--size relation 
    for massive ETGs.

@@

@@

    In Paper~I, we select a sample of 25286 bright galaxies with spectroscopic 
    redshifts or reliable `red-sequence' photometric redshifts (\citealt{Rykoff2014}) 
    at $0.3<z<0.5$. 
    Within this redshift range, we have a large enough volume 
    ($\sim5\times 10^6$ Mpc$^3$) to sample the galaxy stellar mass function above 
    \logms$>11.6$, and we can spatially resolve galaxies profiles to $\sim 5$ kpc 
    ($1.0^{\arcsec}$ corresponds to 4.4 and 6.1 kpc at $z=0.3$ and 0.5, respectively). 
    \song{
    Massive galaxies should experience little structural evolution and 
    size growth between $z=0.5$ and 0.3 ($\sim$1.5 Gyr time span) 
    based on model predictions (e.g., \citealt{Shankar2015}).
    }

@@

   We use these two simple metric masses to explore the \mstar{}-dependence of the 
   fraction of accreted stars and to reveal the diversity of stellar envelopes among 
   massive galaxies. 
   In practice, we also have the full profiles for each galaxy and can cast our 
   results in terms of the full stellar mass profiles. 
   However, in many cases we find it useful to display figures using the simpler 
   \minn{} and \mtot{} quantities. 
   In Figure \ref{fig:m100_m10_color}, we highlight the diversity of galaxies as a 
   function of \minn{} and \mtot{}. 
   Figure \ref{fig:m100_m10_color} shows a subsample of massive galaxies with very 
   similar \minn{} but show a large range of \mtot{}. 
   We use these two aperture masses to guide our comparison of massive galaxies 
   as a function of environment.

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_prof_1}
      \caption{
          The environmental dependence of the stellar mass profiles of massive central 
          galaxies. 
          \textbf{Left}: Halo mass dependence of galaxy \mden{} profiles at fixed 
          `total' stellar mass (\mtot{}). 
          \textbf{Right}: Halo mass dependence of galaxy \mden{} profiles at fixed 
          `inner-mass' (\minn{}). 
          In each plot, we match the two samples so that they share similar 
          distributions of mass and redshift (Appendix~\ref{app:match}).
          We use $R^{1/4}$ as $x$--axis to provide a balanced view of both the central 
          and outer regions of the galaxy.
          Orange and red lines correspond to central galaxies living in 
          haloes with \logmh{} $\geq 14.2$. 
          Black and grey lines correspond to central galaxies living in haloes with 
          \logmh{} $\leq 14.0$. 
          Thin lines show the profiles of individual galaxies, while thick lines show 
          the median profile. 
          The uncertainty on the median profile is given by the shaded region and is 
          computed via bootstrap resampling. 
          Brown lines in the bottom panels show the relative difference between  
          the two median profiles 
          ($\Delta = \log(\mu_{\star, \mathrm{cenHighMh}}) - 
          \log(\mu_{\star, \mathrm{cenLowMh}}$). 
          Errors in the difference between the two profiles are also computed 
          via bootstrap.
          The grey-shaded regions show a Monte Carlo test to assess how likely it is to 
          obtain $\Delta$ from random sub-samples of the data. 
          To compute the grey-shaded regions, we first mix the two samples 
          (\rbcg{} and \nbcg{}), then draw sub-samples of galaxies from the mixed 
          population and compute $\Delta$ in the same fashion as for our fiducial 
          signal. 
          We repeat this process 5000 times.  
          The dark grey--shaded region (light grey--shaded region) shows the 1-$\sigma$ 
          (3-$\sigma$) fluctuations in $\Delta$ from these 5000 draws.
          }
      \label{fig:prof_1} 
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    In this work, we focus on massive galaxies with \mtot{} $>10^{11.6}$~\msun{}. 
    In Paper~I, we demonstrate that this sample is almost mass complete over our full 
    redshift range. 
    In addition to the mass cut above, we also limit our sample to galaxies that live 
    at the centers of their own dark matter haloes -- so-called `central' galaxies. 
    We use the \redm{} \texttt{v5.10} \citep{Rykoff2014, Rozo2015b} cluster catalogue 
    to help us construct two central galaxy samples: one for high mass haloes, and 
    one for low mass haloes.

@@

    First, we build a sample of central galaxies in high mass haloes. 
    We select 68 massive central galaxies from \redm{} clusters with richness
    $\lambda \geq 30$, with central probability $P_{\mathrm{Cen}} \geq 0.7$, and 
    \logmtot{}$ >11.5$ at $0.3 < z < 0.5$ (63/68 have \logmtot{}$ >11.6$). 
    This $\lambda$ limit is chosen to mitigate incompleteness in the cluster catalogue
    at the high end of our redshift window. 
    The $P_{\mathrm{Cen}}$ limit is imposed to limit our sample to central galaxies. 
    \song{
    \citet{Simet2017} present a calibration of the \mhalo{}-$\lambda$ relation for 
    \redm{} clusters using SDSS weak-lensing. 
    Based on this calibration, our sample corresponds to central galaxies living 
    in haloes with \mhalo{}$>10^{14.2}$~\msun{}. 
    This calibration is consistent with several other independent calibrations 
    using different methods (e.g., \citealt{Saro2015, Farahi2016, 
    Melchior2016, Murata2017}). 
    }
    The median richness of the sample is $\lambda \approx 41$ 
    (\logmhalo{}$\approx 10^{14.3}$), and there are 44 central galaxies 
    in clusters with $\lambda>50$ (\mhalo{}$\approx 10^{14.5}$).
    We refer to this sample of \textbf{central galaxies in massive haloes} as 
    the \rbcg{} sample.

    Second, we build a sample of central galaxies in low mass haloes. 
    We begin by excluding all galaxies in \redm{} clusters with $\lambda > 20$.
    \song{
    We convert $\lambda$ to $M_{\mathrm{200b}}$ using the \citet{Simet2017} calibration. 
    For each cluster, we compute $R_{\mathrm{200b}}$ using the \texttt{Colossus} Python 
    package 
    (\citealt{Colossus})\footnote{\url{http://www.benediktdiemer.com/code/colossus/}}
    provided by \citet{Diemer2015}
    } 
    We exclude all galaxies within a cylinder around each cluster, with a radius
    equal to $R_{\mathrm{200b}}$, and a length equal to twice the value of the 
    photometric redshift uncertainty of the cluster (typically around 0.015 to 0.025).
    This second sample is dominated by central galaxies living in haloes with
    $M_{\mathrm{200b}} < 10^{14}$~\msun{}; we refer to this sample as \nbcg{}. \
    There are 833 central galaxies with \logmtot{}$> 11.6$ in this sample.

    Given the high stellar mass, satellite contamination in our sample should be 
    low (e.g., \citealt{Reid2014, Hoshino2015, Saito2016, vanUitert2016}). 
    For instance, the model from \citet{Saito2016} predicts that our \rbcg{} sample 
    should only contain $\sim 7$\% satellites (corresponding to satellites with 
    \logmtot{}$>11.6$ and living in haloes with \logmh$<14.0$).

@@

    Our analysis fails to extract 1-D profiles for $\sim10$\% of 
    \rbcg{} and \nbcg{} galaxies due to ongoing major mergers or projection effects 
    (e.g.\ nearby foreground galaxy or bright stars). 
    We exclude these galaxies from our analysis and this low failure rate should not 
    affect any of our results.

@@

    First, we ask whether the \mden{} profiles of massive central galaxies depend on 
    halo mass at fixed stellar mass.    
    We show comparisons of \mden{} profiles at both fixed \mtot{} and fixed 
    \minn{} (see Figure~\ref{fig:prof_1}). 
    All comparisons are performed with a fixed underlying redshift
    distribution by matching samples in redshift in addition to stellar mass
    (see Appendix~\ref{app:match}, Appendix~\ref{app:redshift}, 
    and Fig~\ref{fig:match} for details).

@@

        \item Massive galaxies matched by \minn{} display a range of \mtot{} values. 
            Those in massive dark matter halos have more prominent outer stellar haloes. 
            The scatter in the outer profiles observed in Figure \ref{fig:prof_1} is 
            an \textit{intrinsic} scatter (not measurement error).

@@

    In summary, we detect a subtle, but robust halo mass dependence of the profiles of 
    massive central galaxies. 
    This dependence could be driven by the fact that massive halos have a larger minor 
    merger rate compared to less massive haloes. 
    Non--dissipative (minor) mergers should not strongly alter inner profiles, but can
    efficiently build up outer haloes (e.g., \citealt{Hilz2013}, \citealt{Oogi2013}).

@@

    \song{
    However, `size' is not a well-defined parameter for massive galaxies with very 
    extended stellar mass distributions. 
    In practice, measurements of the `effective radius', or `half-light radius', depend 
    on resolution, depth, filter, and may also depend on the adopted model for the 
    light profile.  
    This makes comparisons of size measurements among different observations, 
    or between observations and models, uncertain. 
    This is the main reason why we prefer to compare \mden{} profiles directly which 
    completely bypasses the need to consider `size'.
    }

@@

    \song{
    We also compare with results from \citealt{HCompany13} (HC13b; green dashed line), 
    who studied $z\leq 0.09$ central ETGs in $12.5 \le$ \logmh{} $< 15$ haloes. 
    HC13b use the \citet{Yang2007} group catalog to estimate halo mass. 
    In contrast to the present study, HC13b find no environment dependence in the 
    mass--size relation for central galaxies. 
    They obtain effective radii from single-\ser{} model fitting to SDSS 
    images and derive stellar mass based on SED fitting using the BC03 (\citealt{BC03}) 
    synthetic population model. 
    We convert the HC13b \mstar{} estimates from a Kroupa IMF to a Chabrier 
    IMF by applying a constant $-0.05$ dex shift (see \citealt{Bernardi2016a}). 
    We further add $+0.1$dex to the HSC13 stellar masses to account for a systematic 
    offset between BC03 and our FSPS model (see Paper~1). Our overall mass-size relation 
    is in good agreement with HC13a.
    }

@@

    We now explore the environment dependence of galaxy structure using the 
    \mtot{}-\minn{} relation.
    Compared to the mass--size relation, the \mtot{}--\minn{} relation is not plagued 
    by the ambiguity of galaxy `size', and it also enables a more straightforward 
    comparison with numerical simulations.

@@

@@

        \item \song{
            The ellipticity profiles of massive central galaxies do not depend on 
            halo mass at fixed \mtot{} at $R<60$ kpc (upper left panel). 
            }

@@

    Using deep images from the HSC survey, we show that the stellar mass distributions 
    of massive central galaxies at $0.3 < z < 0.5$ depend on halo mass. 
    At fixed total galaxy mass, central galaxies in massive halos have larger 
    half-light radii and host more prominent outer stellar haloes compared to galaxies 
    in low mass haloes (Figure~\ref{fig: fig:scaling_relation}). 
    We also find that the outer stellar haloes ($R>50$ kpc) of massive galaxies show 
    the strongest variations with halo mass.

    \song{
    The two-phase formation scenario can qualitatively explain these results. 
    In this scenario, intense dissipative processes at $z > 2$ are responsible for the 
    formation of \textit{in situ} stars in massive central galaxies. 
    After a rapid quenching of star formation, the subsequent assembly of massive 
    galaxies is dominated by the accretion of satellite galaxies through (mostly) 
    non--dissipative mergers. 
    Dry minor mergers are efficient at depositing \textit{ex situ} stars in the 
    outskirts of massive galaxies (e.g., \citealt{Oogi2013, Bedorf2013}) and hence in 
    building up outer stellar haloes. 
    The fact that minor mergers become more frequent in more massive dark matter 
    haloes could lead to the halo mass dependence of galaxy profiles that we identify 
    in Figure~\ref{fig:prof_1}.
    }

@@

    Figure \ref{fig:scaling_relation} shows that, at fixed total galaxy mass, centrals 
    in high mass haloes have slightly shallower inner \mden{} slopes and lower values 
    of \minn{} compared to those in low mass haloes. 
    \song{
    We have tested that this cannot be solely explained by the choice of a finite 
    aperture (100 kpc) to estimate `total' galaxy mass. 
    Integrating our profiles out to larger radii makes the differences between \rbcg{} 
    and \nbcg{} galaxies on the \mtot{}--\minn{} plane even more significant 
    (see Appendix~\ref{app:robust}). 
    In hydrodynamic simulations, intense dissipative processes help create a 
    self-similar de~Vaucouleurs--like ($n{\sim} 4$) inner density profile 
    (e.g., \citealt{Hopkins2008}). 
    However, there are a variety of physical processes that can shape and alter the 
    inner  profile which we now discuss.
    }
